% Eddie (Hung-Ta Lai) — Resume v8
% Dual positioning: Startup Founder + Hireable Engineer
% Compile with: pdflatex Eddie_Resume_v8.tex

\documentclass[10pt,a4paper]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage{parskip}

\definecolor{accent}{HTML}{1a4d8f}

\hypersetup{colorlinks=true, urlcolor=accent}

% Section formatting
\titleformat{\section}{\large\bfseries\color{accent}}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{8pt}{4pt}

\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=2pt, parsep=0pt}

\newcommand{\role}[3]{\textbf{#1} \hfill \textit{#2} \\ \textit{#3}}
\newcommand{\link}[2]{\href{#1}{\underline{#2}}}

\pagestyle{empty}

\begin{document}

% ============ HEADER ============
\begin{center}
    {\Huge\bfseries Hung-Ta Lai (Eddie)}\\[4pt]
    \small
    \faPhone\ 0983-088-254 \quad
    \faEnvelope\ \href{mailto:eddlai.be10@nycu.edu.tw}{eddlai.be10@nycu.edu.tw} \quad
    \faLinkedin\ \link{https://linkedin.com/in/YOUR-HANDLE}{linkedin} \quad
    \faGithub\ \link{https://github.com/eddLai}{github.com/eddLai}
\end{center}

% ============ TAGLINE ============
\begin{center}
    \textit{Building \textbf{ExoPulse} — closed-loop AI medical exoskeletons for elder mobility.\\
    BMI/HMI researcher at NYCU. Shipping research from lab to clinic.}
\end{center}

% ============ FOUNDER EXPERIENCE ============
\section*{Founder Experience}

\role{ExoPulse}{[YYYY--Present]}{Founder \& CEO --- Technical Lead, team of $\sim$10}

\vspace{2pt}
Closed-loop AI medical exoskeleton for elders and pre-frail individuals,
built on digital-twin simulation and deep reinforcement learning control.

\begin{itemize}
    \item Lead a cross-functional team of $\sim$10 across firmware, ML, mechanical
    design, and clinical coordination. Own the technical roadmap end-to-end:
    D4PG reinforcement learning controller,
    OpenSim + Hill-type digital twin pipeline, embedded firmware on Xilinx KV260 FPGA
    and Nordic IoT, wireless 1 kHz EMG acquisition, and mechanical prototype.
    \item Pitched to US investors at \textbf{Pitch in New York}.
    \link{https://YOUR-PITCH-VIDEO}{Pitch Video} $\cdot$
    \link{https://YOUR-DECK}{Deck}
    \item \textbf{3rd Prize, iCREATE-GSIC Global Competition} (Taiwan representative;
    awarded by HRH the Princess Royal).
    \link{https://YOUR-VIDEO}{Video} $\cdot$
    \link{https://YOUR-PROPOSAL}{Proposal}
    \item Featured on \textbf{PTS National News} (Feb 19, 2025) via joint press
    conference with Taipei Veterans General Hospital (TVGH).
    \link{https://YOUR-NEWS-LINK}{News}
    \item \textbf{Traction:} Active clinical collaborations with \textbf{three hospitals}
    for pilot testing and validation.
\end{itemize}

% ============ RESEARCH EXPERIENCE ============
\section*{Research Experience}

\textbf{NYCU Department of Biomedical Engineering} \hfill \textit{[YYYY--Present]}\\
\textit{Research Assistant across four concurrent projects}

\vspace{4pt}
\textbf{Exoskeleton Power Augmentation (HMI) — Tech Lead}
\begin{itemize}
    \item Built embedded control stack on Xilinx FPGA KV260+KD240 and Nordic IoT
    (migrated from ESP32) for real-time closed-loop exoskeleton control.
    \item Implemented D4PG distributed deep RL for human–machine interaction;
    integrated with OpenSim/SCONE musculoskeletal simulation and EMG-based
    motion intent prediction.
    \item \textbf{Independently built} a wireless EMG acquisition system at 1 kHz
    sampling outside lab scope. First-author paper at GCBME.
    \link{https://YOUR-ABSTRACT}{Abstract} $\cdot$
    \link{https://YOUR-SLIDES}{Slides}
\end{itemize}

\textbf{Markerless Motion Capture — Tech Lead}
\begin{itemize}
    \item Built AI-based 3D human pose estimation pipeline; validated against
    Vicon ground truth.
    \item Shipped real-time video-streaming web UI and one-click Docker deployment
    adopted by lab researchers.
    \item Work featured in NYCU $\times$ TVGH joint press conference, Feb 2025.
    \link{https://YOUR-PRESS-VIDEO}{Press Conference}
\end{itemize}

\textbf{Neural Decoding (BMI/BCI)}
\begin{itemize}
    \item Conducted rodent behavior experiments for neural signal decoding using
    Temporal Convolutional Networks (TCN) for time-series regression.
    \item Participated in electrode fabrication and implantation; designed 3D-printed
    behavioral apparatus (sliding rail, rat behavior box, water supply platform).
    \link{https://YOUR-RAIL}{Sliding Rail} $\cdot$
    \link{https://YOUR-BOX}{Behavior Box}
\end{itemize}

\textbf{Biochemical Wearable Sensor}
\begin{itemize}
    \item Integrated MCU-controlled TI LMP91000 electrochemical AFE; performed
    circuit simulation and PCB layout for wearable real-time health monitoring.
    \item \textbf{1st Prize (National), MOE Innovation \& Entrepreneurship Competition}.
    \link{https://YOUR-PITCH}{Pitch} $\cdot$
    \link{https://YOUR-DECK}{Deck}
\end{itemize}

% ============ SKILLS ============
\section*{Technical Skills}

\begin{itemize}[leftmargin=1.2em]
    \item[] \textbf{Core:} Reinforcement Learning (D4PG), BMI/HMI, Embedded AI, Digital Twins
    \item[] \textbf{Hardware:} Xilinx FPGA (KV260/KD240, Vivado/Vitis), Nordic, ESP32, MSP430, Jetson Nano, Raspberry Pi
    \item[] \textbf{Signal \& Simulation:} EMG (custom 1 kHz rig), LFP, spike sorting, OpenSim, SCONE, Hill-type muscle models
    \item[] \textbf{ML / CV:} PyTorch, TCN, Transformers, markerless 3D pose estimation
    \item[] \textbf{Software \& DevOps:} C++, Python, JavaScript, Docker, Git, Slurm, ROS, X11
    \item[] \textbf{Hardware CAD:} KiCAD, AutoCAD, Shape3D, 3D printing, PCB layout
    \item[] \textbf{Other:} VR (Meta Quest 3), NSTC project budget \& BOM management
\end{itemize}

% ============ EDUCATION ============
\section*{Education}

\textbf{National Yang Ming Chiao Tung University (NYCU)} \hfill \textit{[YYYY--YYYY]}\\
\textit{BS + MS, Biomedical Engineering — Five-year Integrated 4+1 Program (in progress)}

% ============ AWARDS ============
\section*{Selected Awards \& Recognition}

\begin{itemize}
    \item \textbf{2024 NSTC College Student Research Scholarship} — Multimodal neural
    decoding of posture and gait via the posterior parietal cortex–M2 pathway.
    \link{https://YOUR-REPORT}{Final Report}
    \item \textbf{Outstanding Paper Award, Chinese Institute of Engineers (CIE)}
    \item \textbf{2nd Prize, NVIDIA AIoT Challenge} — Jetson Nano edge-AI CV application
    \item \textit{Additional: Macronix Competition (Hip Exoskeleton + AR), Matlab Poster
    Competition (RL for exoskeleton closed-loop control).}
\end{itemize}

% ============ TEACHING & LEADERSHIP ============
\section*{Teaching \& Leadership}

\begin{itemize}
    \item \textbf{Advanced Teaching Assistant \& Course Designer}, Embedded Systems
    and C++ Programming, NYCU BME. Mentored students on MSP430 development;
    designed lab sessions. \link{https://YOUR-PORTFOLIO}{Teaching Portfolio}
    \item \textbf{Preliminary Interviewer}, Taiwan Experience Education Program (TEEP)
    — screened exchange student candidates for exoskeleton collaboration.
    \item \textbf{Exhibitor}, International Medical Technology Exhibition (Nangang,
    Taipei), co-exhibited with Institute for Information Industry (III).
    \item \textbf{Event Lead}, BME Orientation Camp and BME Night, NYCU.
    \item NYCU varsity Soft Tennis (National University Games, Men's Singles);
    completed Taipei–Kaohsiung one-day cycling challenge.
\end{itemize}

% ============ CLOSING ============
\vspace{6pt}
\hrule
\vspace{4pt}
\small
\textbf{Open to:} healthtech investor conversations (pre-seed/seed) $\cdot$
clinical collaborators in rehab and geriatrics $\cdot$
full-time engineering roles in BMI, robotics, or medical devices.

\end{document}
